A Language's Unigram Entropy Distribution Predicts Self-Paced Reading Times

### 2018-12-21 cogsci/position-info.Rmd
updated background and our analysis in Cogsci abstract

abstract: 
    "We aim to provide evidence against the popular Uniform Information Density 
    (Jaeger, 2010) and wrap-up effect (Kuperman et al., 2010) hypotheses using cross-linguistic 
    evidence from speech, text and eye-tracking corpora."

@@

The average distribution of information in English sentences-what is it? Genzel & Charniak (2002) looked at the log-probability of words occurring in sentences as you proceed through a paragraph or article and found that less common/less likely words occurred more frequently as you moved through the text. The relationship they found was roughly an affine linear function, leading them to propose the *constant entropy rate* (CER) principle: the entropy of words in a sentence, i.e. the uncertainty about what words will appear in a sentence, will increase at a constant, linear rate through a paragraph. This idea was used by Aylett & Turk (2004), Levy & Jaeger (2007) and Frank & Jaeger (2008) among others. The CER principle was adapted by Jaeger (2010) into the *uniform information density* (UID) principle: uniformation is evenly spread throughout a sentence. From a theoretical standpoint, this makes sense as the optimal distribution for information throughout a sentence: if you miss any word I’ve said, the rest of the information in the sentence is intact, and you lose no more than if you miss any other word I’d have said.

@@

```{r yunigram, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "English entropy distribution for three sentence lengths from BNC"}
img <- png::readPNG("figs/yunigram.png")
grid::grid.raster(img)
```

This diverges from the UID account, which would predict a simple affine function. 
Our replication with CHILDES. Conditional entropy and mutual information. Link with Thiessen & Onnis (to appear). Mention Ferrer-i-Cancho (2017), which provides a theoretical basis for the end of the sentence being the center of information. 
Cross-linguistic variation. Our Wikipedia analysis
Link with Kuperman et al. (2010). Talk about challenges to the wrap-up account. Consequences for eye-tracking. Talk about Zhan and Levy (2018) and how current work in eye-tracking and language processing disputes the UID account.

>>>>

abstract: 
    "We provide evidence against the Uniform Information Density (Jaeger, 2010) 
    and wrap-up effect hypotheses."

@@

A major line of research in the current century has asked how speakers and writers distribute information in the linguistic material they produce. This begins with Claude Shannon in the years after World War II. Shannon (1948) defined "information" as a "reduction in uncertainty". Shannon followed by quantifying uncertainty in his measure of *entropy*: the amount of uncertainty on the outcome of a random variable. Shannon proposed that the most efficient method of sending information through a noisy channel is at a constant rate. Genzel & Charniak (2002) apply this principle to human communication: if people communicate information through speech and text optimally, then we should transmit information to one another at a constant rate. Genzel & Charniak created a distribution of estimates for sentence-level entropy, each sentence taken without context, for newspaper articles from the Penn Treebank corpus. Obtaining a roughly monotonically increasing linear distribution, Genzel & Charniak proposed the *Constant Entropy Rate* (CER) principle: the entropy rate in speech and text with context should be constant as sentence number increases. Aylett & Turk (2004) proposed a similar principle for the phonological level.

Jaeger (2010) extends the CER principle to all levels of human communication: the *Uniform Information Density* (UID) hypothesis. Jaeger argues that speakers will try to distribute information more evenly over the course of an utterance, to be as close to channel capacity (in a Shannon sense) as possible. In particular, Jaeger singles out the production of "that" at the beginning of relative clauses in English and the use of contractions such as "he's" and "you're" versus "he is" and "you are" as instances where higher information density in the clause elicits the production of more material by speakers.

The *wrap-up effect* is a popular hypothesis within the eye-tracking community. The hypothesis states that, in written text, sentence-final words are processed more slowly on average then sentence-medial or sentence-initial words, due to readers integrating information from the entire sentence in order to form a final, coherent thought expressed by the sentence, among other reasons. With these two ideas, information production distribution in spoken and written communication, and information integration in reading written texts, we move on to discuss cross-linguistic differences in the distribution of information across sentences.

@@

# Our Methods

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations. We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains conversations between three young children (over 1.5 years old and under 6 years old) and their families in the home. The Providence corpus contains transcriptions of audio/video files which recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker (child and non-child) and each sentence length within those divisions and computed the unigram entropy measure for each position within those sentence lengths. Plots for the entropy distributions are below. The adult and child unigram entropy distributions track one another extremely well, with the child distribution for each sentence length having relatively lower entropy.

```{r brown_PE, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Brown corpus entropy"}
img <- png::readPNG("figs/positional_entropy_brown.png")
grid::grid.raster(img)
```

```{r providence_PE, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Providence corpus unigram entropy"}
img <- png::readPNG("figs/Prov_corpus_result.png")
grid::grid.raster(img)
```

Unlike a UID account

We found a similar distribution for Spanish and German corpora from CHILDES. The Spanish corpus we used was the XXX and the German corpus we used was the XXX.

### 2018-12-21 cogsci/position-info.tex
updated background and our analysis in Cogsci abstract

\begin{abstract}
The abstract should be one paragraph, indented 1/8 inch on both sides,
in 9 point font with single spacing. The heading Abstract should be 10
point, bold, centered, with one line space below it. This one-paragraph
abstract section is required only for standard spoken papers and
standard posters (i.e., those presentations that will be represented by
six page papers in the Proceedings).

@@

The average distribution of information in English sentences-what is it?
Genzel \& Charniak (2002) looked at the log-probability of words
occurring in sentences as you proceed through a paragraph or article and
found that less common/less likely words occurred more frequently as you
moved through the text. The relationship they found was roughly an
affine linear function, leading them to propose the \emph{constant
entropy rate} (CER) principle: the entropy of words in a sentence,
i.e.~the uncertainty about what words will appear in a sentence, will
increase at a constant, linear rate through a paragraph. This idea was
used by Aylett \& Turk (2004), Levy \& Jaeger (2007) and Frank \& Jaeger
(2008) among others. The CER principle was adapted by Jaeger (2008) into
the \emph{uniform information density} (UID) principle: uniformation is
evenly spread throughout a sentence. From a theoretical standpoint, this
makes sense as the optimal distribution for information throughout a
sentence: if you miss any word I've said, the rest of the information in
the sentence is intact, and you lose no more than if you miss any other
word I'd have said. Description of the UID perspective and what it
predicts for entropy distributions and what that means.

\subsection{Yu challenge}\label{yu-challenge}

The UID perspective is challenged in Yu et al. (2016), by performing an
analysis of entropy by position in the text portion of the British
National Corpus. They use the following formula for each word position X
of sentences of fixed length k from the corpus, where each i is a word
occurring in position X and pi is the number of times word i occurs in
position X divided by the number of total words that occur in position X
i.e.~the number of sentences of length k.

@@

This diverges from the UID account, which would predict a simple affine
function. Our replication with CHILDES. Conditional entropy and mutual
information. Link with Thiessen \& Onnis (to appear). Mention
Ferrer-i-Cancho (2017), which provides a theoretical basis for the end
of the sentence being the center of information. Cross-linguistic
variation. Our Wikipedia analysis Link with Kuperman et al. (2010).
Consequences for eye-tracking. Talk about Zhan and Levy (2018) and how
current work in eye-tracking and language processing disputes the UID
account. Our eye-tracking experiment.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -0.02 & 0.10 & -0.2 & 0.82 \\ 
  x & 1.95 & 0.10 & 19.2 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

>>>>

\begin{abstract}
We provide evidence against the Uniform Information Density (Jaeger,
2010) and wrap-up effect hypotheses.

@@

A major line of research in the current century has asked how speakers
and writers distribute information in the linguistic material they
produce. This begins with Claude Shannon in the years after World War
II. Shannon (1948) defined ``information'' as a ``reduction in
uncertainty''. Shannon followed by quantifying uncertainty in his
measure of \emph{entropy}: the amount of uncertainty on the outcome of a
random variable. Shannon proposed that the most efficient method of
sending information through a noisy channel is at a constant rate.
Genzel \& Charniak (2002) apply this principle to human communication:
if people communicate information through speech and text optimally,
then we should transmit information to one another at a constant rate.
Genzel \& Charniak created a distribution of estimates for
sentence-level entropy, each sentence taken without context, for
newspaper articles from the Penn Treebank corpus. Obtaining a roughly
monotonically increasing linear distribution, Genzel \& Charniak
proposed the \emph{Constant Entropy Rate} (CER) principle: the entropy
rate in speech and text with context should be constant as sentence
number increases. Aylett \& Turk (2004) proposed a similar principle for
the phonological level.

Jaeger (2010) extends the CER principle to all levels of human
communication: the \emph{Uniform Information Density} (UID) hypothesis.
Jaeger argues that speakers will try to distribute information more
evenly over the course of an utterance, to be as close to channel
capacity (in a Shannon sense) as possible. In particular, Jaeger singles
out the production of ``that'' at the beginning of relative clauses in
English and the use of contractions such as ``he's'' and ``you're''
versus ``he is'' and ``you are'' as instances where higher information
density in the clause elicits the production of more material by
speakers.

The \emph{wrap-up effect} is a popular hypothesis within the
eye-tracking community. The hypothesis states that, in written text,
sentence-final words are processed more slowly on average then
sentence-medial or sentence-initial words, due to readers integrating
information from the entire sentence in order to form a final, coherent
thought expressed by the sentence, among other reasons. With these two
ideas, information production distribution in spoken and written
communication, and information integration in reading written texts, we
move on to discuss cross-linguistic differences in the distribution of
information across sentences.

The UID hypothesis

\subsection{UID challenges}\label{uid-challenges}

More recent work has stood out in contrast to the traditional UID
perspective. Zhan and Levy (2018) study Mandarin Chinese classifier use,
and find that the use of specific classifier, versus general
classifiers, appears more often in cases where the production of the
corresponding noun is more difficult than when the production is easier,
as would be predicted by UID. The UID perspective is challenged in Yu et
al. (2016), by performing an analysis of entropy by position in the text
portion of the British National Corpus. They use the following formula
for each word position X of sentences of fixed length k from the corpus,
where each i is a word occurring in position X and pi is the number of
times word i occurs in position X divided by the number of total words
that occur in position X i.e.~the number of sentences of length k.

@@

\section{Our Methods}\label{our-methods}

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora
database of spoken adult-child conversations. We first used the Brown
and Providence English corpora from CHILDES. The Brown corpus contains
conversations between three young children (over 1.5 years old and under
6 years old) and their families in the home. The Providence corpus
contains transcriptions of audio/video files which recorded interactions
between children between 1 and 3 years old and their parents in the
home.

{\centering \includegraphics{figs/brown_PE-1}

\caption[Brown corpus entropy]{Brown corpus entropy}\label{fig:brown_PE}
\end{figure*}
\end{CodeChunk}

{\centering \includegraphics{figs/providence_PE-1}

\caption[Providence corpus unigram entropy]{Providence corpus unigram entropy}\label{fig:providence_PE}
\end{figure*}
\end{CodeChunk}

We found a similar distribution for Spanish and German corpora from
CHILDES. The Spanish corpus we used was the XXX and the German corpus we
used was the XXX.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -0.10 & 0.11 & -0.9 & 0.37 \\ 
  x & 1.97 & 0.12 & 16.6 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}
